---
title: "R Notebook"
output: html_notebook
---

```{r}

#install.packages ("purrr")
```


```{r}
library(data.table)

library(sandwich)
library(lmtest)

library(AER) 

library(ggplot2) 
library(patchwork)
library(stargazer)
library(dplyr)
library(janitor)
```

```{r}
d_j <- fread("dataset_tmp.csv")
```


```{r}

d_j[,q1_right := ifelse((Chart_Control1 == 'Right' | Chart_Control2 == 'Right' | Chart_Treat1 == 'Right' | Chart_Treat2 == 'Right'), 1, 0) ]

d_j[,q1_treat := ifelse( (Chart_Treat1 != "" | Chart_Treat2 != ""), 1, 0) ]

```



```{r}
d_j[,q2_right := ifelse(Array_Control1 == 'Right' | Array_Control2 == 'Right' | Array_Control3 == 'Right' | Array_Treat1 == 'Right' | Array_Treat2 == 'Right' | Array_Treat3 == 'Right', 1, 0) ]

d_j[,q2_treat := ifelse( Array_Treat2  != "" | Array_Treat1  != "" | Array_Treat3 != "", 1, 0) ]

d_j[,all_q_right := q1_right + q2_right ]

#now not significant
d_j[,esl_treat := ifelse( ESL == "Yes" & (q2_treat == 1 | q1_treat == 1), 1, 0) ]

tabyl(d_j, q1_right, q2_right)
```


Got the first chart right/wrong:

```{r}
chart1_wrong <- nrow(d_j[(q1_right == 0 & q1_treat == 1),]) 
chart1_right <- nrow(d_j[(q1_right == 1 & q1_treat == 1),]) 
chart1_treated <- nrow(d_j[q1_treat == 1,])
print(chart1_wrong / chart1_treated)
print(chart1_right / chart1_treated)
```

```{r}
chart2_wrong <- nrow(d_j[q2_right == 0 & q2_treat == 1,])
chart2_right <- nrow(d_j[q2_right == 1 & q2_treat == 1,])
print(chart2_wrong / nrow(d_j[q2_treat == 1]))
print(chart2_right / nrow(d_j[q2_treat == 1]))
```

So chart1 is almost 5x harder than chart2. This makes sense: pie charts suck. Let's look at simple stuff:


```{r}
simple_model <- lm(all_q_right ~ q1_treat + q2_treat, data = d_j)
stargazer(simple_model,
          se = list(sqrt(diag(vcovHC(simple_model)))),
          type = 'text',
          header = F)
```

q2 is definitely easier as a chart.

```{r}
esl_model <- lm(all_q_right ~ q1_treat + q2_treat + as.factor(ESL == "Yes"), data = d_j)

stargazer(esl_model,
          se = list(sqrt(diag(vcovHC(esl_model)))),
          type = 'text',
          header = F)
```

Q1 doesn't make a difference, Q2 does, with our bad data removed ESL doesn't. 

Does ESL affect the two questions separately? We'll look at interaction effects:

```{r}
q1_esl_model <- lm(q1_right ~ q1_treat * as.factor(ESL == 'Yes'), data = d_j)

q2_esl_model <- lm(q2_right ~ q2_treat * as.factor(ESL == 'Yes'), data = d_j)

stargazer(q1_esl_model, q2_esl_model,
          #se = list(sqrt(diag(vcovHC(q1_esl_model)))),
          type = 'text',
          header = F)
```

No difference really. Are the groups the same?
 
```{r}
proportions_table = table(d_j[ESL=="No",], d_j[ESL=="Yes",])
chisq.test(proportions_table)
```
 
Looks like our ESL folks are statistically the same as our non. How about our chart strugglers?

```{r}
proportions_table_2 = table(d_j[q1_treat == 1 & q1_right == 0,], d_j[q2_treat == 1 & q2_right == 0,])
chisq.test(proportions_table_2)
```

Treated/non-treated?

```{r}
treated_groups = table(d_j[q1_treat == 1,], d_j[q2_treat == 1,])
chisq.test(treated_groups)
```

Also, different.
